Semi-parametric generalized linear model for correlated binary data

### 2022-03-14 nuweb/SPGLM.tex
Change starting value for f0

\begin{flushleft} \small\label{scrap11}\raggedright\small
\NWtarget{nuweb10b}{} $\langle\,${\itshape Set starting values}\nobreak\ {\footnotesize {10b}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  betas <- NULL@\\
\mbox{}\verb@  pooled <- CorrBin::CBData(data.frame(Trt = "All", NResp = Y[,1], ClusterSize = rowSums(Y), Freq=ceiling(weights)), @\\
\mbox{}\verb@                    trt="Trt", clustersize="ClusterSize", nresp="NResp", freq="Freq")@\\
\mbox{}\verb@  est <- CorrBin::mc.est(pooled)@\\
\mbox{}\verb@  referencef0 <- est$Prob[est$ClusterSize == N]@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  @\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.

>>>>

\begin{flushleft} \small\label{scrap11}\raggedright\small
\NWtarget{nuweb10b}{} $\langle\,${\itshape Set starting values}\nobreak\ {\footnotesize {10b}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  betas <- NULL@\\
\mbox{}\verb@  #pooled <- CorrBin::CBData(data.frame(Trt = "All", NResp = Y[,1], ClusterSize = rowSums(Y), Freq=ceiling(weights)), @\\
\mbox{}\verb@  #                  trt="Trt", clustersize="ClusterSize", nresp="NResp", freq="Freq")@\\
\mbox{}\verb@  #est <- CorrBin::mc.est(pooled)@\\
\mbox{}\verb@  #referencef0 <- est$Prob[est$ClusterSize == N]@\\
\mbox{}\verb@  referencef0 <- rep(1/(N+1), N+1)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  @\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.
